This analysis has been made possible by a wide array of friends, family, colleagues, and collaborators. I would firstly like to thank my supervisors, Dave Wark and Giles Barr, for their support, knowledge, and expertise which have allowed me to reach this point. I would also like to give gratitude to all the students \textendash \vspace{1mm} Charles, Tomislav, Aidan, Alex, Laurence, Soniya, Ciaran, Kang, Tom, Federico, John, and Weijun \textendash \vspace{1mm} in making the office an enjoyable place to work. Furthermore, I am appreciative of all the help and support which Phil has given me throughout this analysis. Thanks should be given to Kirsty and Patrick who have provided interesting physics discussions along with aiding the writing-up process. 

This analysis has been developed within the MaCh3 fitting framework, and I am thankful for the support of the group throughout this analysis. Particular gratitude is expressed to Patrick Dunne, Asher Kaboth, Ed Atkin, and Kevin Wood for their helpful insights into the world of Bayesian oscillation analyses. Without their input, this analysis would not have been achievable. Special thanks are owed to Clarence Wret, for his friendship and support throughout my studies. Whether it be for discussing the minute details of an interaction model, aiding with my late-night coding problems, or convening the T2K+SK joint oscillation analysis group, he has played a crucial role in the progression of this analysis.

The results of this thesis combine the efforts of many collaborators within the T2K and SK experiments, of which there are far too many to name and I owe my thanks to them all. I am particularly grateful to the members of the T2K+SK joint oscillation analysis group and especially the convenors, Christophe Bronner, Megan Friend, Mike Wilking, and Clarence. Their invaluable help has severely progressed the analysis. The analysis tools developed within this thesis have been compared to the P-Theta analysis, and thanks are owed to Lukas Berns and Junjie Xia for their help and support in this work. Additional appreciation goes to Cris Vilela and Roger Wilking for their significant input and general knowledge of the SK and T2K analyses.

This thesis would not have been possible without the computational resources provided by several facilities: Compute Canada (now Digital Research Alliance of Canada) Cedar, Beluga, Graham, and Narval clusters; SCARF cluster facilitated by the STFC; and RAL PPD computing group. I would also like to acknowledge Magdalen College for their financial support throughout this analysis, via the Oxford\textendash Leon E and Iris L Beghian Graduate Scholarship.

Finally, I am appreciative of my family and friends for all the help and encouragement I have received throughout my DPhil. I would like to particularly thank April for all the sacrifices she has made throughout my analysis. I am grateful for her continued support and patience during the writing-up process and for her putting up with my absence during my time in Japan.
